%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Anirudh} \headerlastnamestyle{Iyer} \\
	\vspace{2mm}
	{\faEnvelope\ a24iyer@uwaterloo.ca} | {\faMobile\ (905) 616-1772} | {\faMapMarker\ Waterloo, ON} | {\faLink\ anirudhi.github.io}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BCS in Computer Science}
	{University of Waterloo}
	{Waterloo, ON}
	{Sep 2016 – Expected Apr 2021}
	{}
\end{cventries}

\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Work Experience}
\begin{cventries}
	\cventry
	{SOFTWARE ENGINEERING INTERN}
	{Paravision}
	{San Francisco, CA (Remote)}
	{May 2020 – Aug 2020}
	{\begin{cvitems}
		\item {Improved inference time by 20\% in a high performance face recognition SDK by converting TensorRT engines to ONNX.}
		\item {Developed a system to compile and distribute releases at scale for Paravision’s primary C++ SDK with CircleCI.}
		\item {Reduced GPU utilization by 15\% in real time streaming app by detecting unused frames and implementing NMS.}
		\item {Created production ready, multi stage Docker images to use for Computer Vision deployment at scale.}
		\end{cvitems}}
	\cventry
	{SOFTWARE ENGINEERING INTERN}
	{SelfMade}
	{New York, NY}
	{May 2019 – Aug 2019}
	{\begin{cvitems}
		\item {Created a referral system and targeted onboarding to increase user aquisition for SelfMade Collabs by 400\%.}
		\item {Built REST APIs in Meteor/Node.js to handle multi-user chat, Instagram giveaways and several other collaboration tools.}
		\item {Developed components in React/Redux for user profile creation and brand filtering.}
		\item {Optimized API worker instances on EC2 to handle over 200\% more concurrent jobs from \textgreater{}50 SQS queues.}
		\end{cvitems}}
	\cventry
	{SOFTWARE ENGINEERING INTERN}
	{Shopify}
	{Ottawa, ON}
	{Sep 2018 – Dec 2018}
	{\begin{cvitems}
		\item {Migrated the Shopify Logistics admin platform from Ruby on Rails to a GraphQL, React.js/Typescript stack.}
		\item {Implemented a new refunds flow in React that could handle orders with \textgreater{}1000 line items and multiple shipping locations.}
		\item {Optimized refund query algorithm to filter out stale data, reducing data sent to the web client by 30\%.}
		\item {Architected GraphQL APIs and client interfaces to allow the editing of orders, the most requested feature in Shopify.}
		\end{cvitems}}
	\cventry
	{WEB DEVELOPMENT INTERN}
	{Mani Wonders}
	{Toronto, ON}
	{Jan 2018 – Apr 2018}
	{\begin{cvitems}
		\item {Refactored their primary ecommerce portal resulting in 12x faster load times and an 80\% reduction in redundant data being loaded.}
		\item {Introduced version control management and drastically sped up developer productivity by setting up a CI pipeline.}
		\end{cvitems}}
	\cventry
	{3D DESIGN AND FIRMWARE DEVELOPER}
	{Inksmith}
	{Kitchener, ON}
	{May 2017 – Aug 2017}
	{\begin{cvitems}
		\item {Developed an extensible Arduino based robotics framework consisting of low cost, 3D printed parts for educational use.}
		\item {Designed a variety of CAD models for various client needs, with optimizations for additive manufacturing.}
		\end{cvitems}}
	\cventry
	{HARDWARE AND FIRMWARE DEVELOPER}
	{Edgebotix}
	{Singapore}
	{Feb 2016 – Aug 2016}
	{\begin{cvitems}
		\item {Developed EBot 2.0 from design to delivery within a 3 month time frame, while reducing cost by 80\%}
		\item {Designed the PCB and firmware for the robot on the TI-CC3200 platform using embedded-C.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages:  & {\skill{ C++, Python, Java, Javascript ES6, Golang, PHP, Lisp, Bash, C}} \\
		Technologies:  & {\skill{ React, Node, Docker, MongoDB, Postgres, CircleCI, TensorRT, Redis, gRPC/Protobuf, Meteor, AWS, Enzyme}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}


\ 
\end{document}